Outline paper - Multiple imputation for statistical disclosure control: Creating synthetic datasets with *mice*

### 2021-01-11 mice_synthesizing/paper.Rmd

By default, `mice` imputes all values that are coded as missing in the dataset. Using the `where` parameter within the mice function, one can choose to impute any value in the dataset. As input, the `where` parameter requires a matrix of the same dimensions of the data, (i.e., a $n \times k$ matrix, with $n$ the number of observations in the collected data) containing logical values.

>>>>

By default, `mice` imputes all values that are coded as missing in the dataset. However, using the `where` parameter within the `mice`-function, one can choose to impute any value in the dataset. As input, the `where` parameter requires a matrix of the same dimensions as the data, (i.e., a $n \times k$ matrix, with $n$ the number of observations in the collected data) containing logicals $z_{jk}$ that indicate which cells are selected to have their values replaced. This approach allows to overimpute a subset of the observed data, or the observed data as a whole, resulting in a dataset that partly or completely consists of synthetic values.
